R for Clinical Study Reports and Submission

### 2022-03-20 submission-package.Rmd

x <- available.packages(contriburl = contrib.url("https://mran.microsoft.com/snapshot/2021-08-06/"))
df2$version <- x[match(df2$package, x[, "Package"]), "Version"]

>>>>

# # Commented out as the snapshot availability is not guaranteed
# x <- available.packages(contriburl = contrib.url("https://mran.microsoft.com/snapshot/2021-08-06/"))
# df2$version <- x[match(df2$package, x[, "Package"]), "Version"]
df2$version <- c("0.2.0", "2.4.3", "1.0.7", "1.1.3", "1.6.2-1", "0.3.0")
